### 2014-02-22 thesis/src/chapters/chapter-implementation.tex
Thesis: implementation scenarios

\newpage
\begin{figure}[!ht]
  \begin{center}
    \includegraphics{chapter-implementation/hlo-deployment}
  \end{center}
  \caption{System's deployment diagram}
  \label{fig:hlo-deployment}
\end{figure}
\newpage

@@

 \item analysis - Aggregated data is analysed against client defined policy. Policies (e.g. listing Y) are based on a threshold model, denoting a valid range for a resource measurement. Hence, its evaluation results in \texttt{FITS, LESSER, GREATER}.

@@

Not enough slaves to handle load & \texttt{GREATER\_CPU} (slave) & \texttt{INSUFFICIENT\_SLAVES} &  Add slave \\ \hline
Slaves are not fully occupied & \texttt{LESSER\_CPU} (slave) & \texttt{REDUNDANT} &  Remove slave \\ \hline
Master is overly engaged & \texttt{GREATER\_CPU} (master) & \texttt{OVERLOADED\_MASTER} &  None \\ \hline
Stack is healthy & \texttt{FITS\_CPU} & \texttt{HEALTHY} & None \\ \hline

@@

Figure X portrays above-mentioned sequence of steps.

@@

% darek
\section{Cloud provider}
\subsection{Introduction}
What cloud provider is responsible for is:
\begin{itemize}
 \item deploying, destroying, monitoring virtual machine
 \item deploying, destroying a stack (group of correlated virtual machines)
\end{itemize}

@@

Figure XXX shows exemplary deployment of OpenNebula along with involved components.

% ?
\section{Exemplary scenarios}

\subsection{Service deployment}

\subsection{Scaling application}

\subsection{Scaling application across multiple cloud providers}

\section{Summary}

>>>>

\begin{figure}[!ht]
  \begin{center}
    \includegraphics{chapter-implementation/hlo-deployment}
  \end{center}
  \caption{System's deployment diagram}
  \label{fig:hlo-deployment}
\end{figure}

@@

 \item analysis - Aggregated data is analysed against client defined policy. Policies (e.g. listing ref{lst:service-spec-test-deployment-time}) are based on a threshold model, denoting a valid range for a resource measurement. Hence, its evaluation results in \texttt{FITS, LESSER, GREATER}.

@@

Not enough slaves to handle load & \texttt{GREATER\_CPU} (slave) & \texttt{INSUFFICIENT\_SLAVES} &  Add slave \\ \hline
Slaves are not fully occupied & \texttt{LESSER\_CPU} (slave) & \texttt{REDUNDANT\_SLAVE} &  Remove slave \\ \hline
Master is overly occupied & \texttt{GREATER\_CPU} (master) & \texttt{OVERLOADED\_MASTER} &  None \\ \hline
Master is not occupied & \texttt{LESSER\_CPU} (master) & \texttt{UNOCCUPIED\_MASTER} &  None \\ \hline
Stack is healthy & \texttt{FITS\_CPU} & \texttt{HEALTHY} & None \\ \hline

@@

Figure \ref{fig:stack-lifecycle-seq} portrays above-mentioned sequence of steps.

\begin{figure}[!ht]
  \begin{center}
    \includegraphics{chapter-implementation/stack-lifecycle-seq}
  \end{center}
  \caption{Sequence diagram illustrating stack manager control loop}
  \label{fig:stack-lifecycle-seq}
\end{figure}

@@

% darek
\section{Cloud provider}
What cloud provider is responsible for is:
\begin{itemize}
 \item deploying, destroying, monitoring virtual machine
 \item deploying, destroying a stack (group of correlated virtual machines)
\end{itemize}

@@

Figure \ref{fig:cloud-provider-deployment} shows exemplary deployment of OpenNebula along with involved components.

\begin{figure}[!ht]
  \begin{center}
    \includegraphics{chapter-implementation/cloud-provider-deployment}
  \end{center}
  \caption{Cloud provider's deployment diagram}
  \label{fig:cloud-provider-deployment}
\end{figure}

\newpage
\section{Exemplary scenarios}

\subsection{Service deployment}
Diagram \ref{fig:case-deployment-seq} depicts sequence of steps involved in service deployment. Such request is triggered by a cloud client and involves multiple cloud provider. Consequently, cloud broker selects best offer for its client.

\begin{figure}[!ht]
  \begin{center}
    \includegraphics[width=\textwidth]{chapter-implementation/case-deployment-seq}
  \end{center}
  \caption{Deployment service - sequence diagram}
  \label{fig:case-deployment-seq}
\end{figure}

\subsection{Scaling application}
Figure \ref{fig:scaling-1cp-seq} illustrates control loop that engages container and stack manager and results in horizontal scaling. This is due to the fact that computing node, where container is deployed, does not have enough resources to perform vertical scaling.

\begin{figure}[!ht]
  \begin{center}
    \includegraphics[width=\textwidth]{chapter-implementation/scaling-1cp-seq}
  \end{center}
  \caption{Scaling within a single cloud provider - sequence diagram}
  \label{fig:scaling-1cp-seq}
\end{figure}

\subsection{Scaling application across multiple cloud providers}
That scenario employs all layers of implemented system: container, stack, cloud instance managers and cloud broker. Similarly to a previous case, policy is violated what results in attempt to scale vertically. This is, however, not possible and hence stack container checks if there are enough resources for a horizontal scaling. As this is not the case, request is passed to cloud instance manager and then cloud broker to deploy container on another cloud. This scenario is also known as a cloud bursting.

\begin{figure}[!ht]
  \begin{center}
    \includegraphics[width=\textwidth]{chapter-implementation/scaling-2cp-seq}
  \end{center}
  \caption{Scaling across two cloud provider - sequence diagram}
  \label{fig:scaling-2cp-seq}
\end{figure}

\newpage
\section{Summary}
